Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-02-06 uca_radio_eclipse_jurpa.tex
Adding a title (this can be changed later.)
Created a foloder with the different sections to resude clutter on the main file, and added abstract.

\title{}% Force line breaks with \\

@@

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. It is used for
secondary publications and for information retrieval purposes.
\end{abstract}

>>>>

\title{Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.}% Force line breaks with \\

@@

\begin{abstract}
\input{sections/abstract}

\end{abstract}
